---
title: "Report of the 2022 EUR Open Science Survey"
author: '[Dr. Lizette Guzman-Ramirez](https://www.linkedin.com/in/drlizguzman/), [Dr. Antonio Schettino](https://antonio-schettino.com/)'
date: 2022-05-26
output:
  bookdown::html_document2:
    # # appearance
    # # table of content
    # # code
    # # figures
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true  
    number_sections: false
    # code_folding: true
    fig_width: 8
    fig_height: 8
    fig_caption: true
editor_options: 
  chunk_output_type: console
---

```{r doc-setup, include = FALSE}

# RNG
seed_proj <- 100
set.seed(seed_proj)

### install packages
# install.packages("bookdown")
# install.packages("knitr")
# install.packages("kableExtra")
# install.packages("here")
# install.packages("tidyverse")

### load packages
library(bookdown)
library(knitr)
library(kableExtra)
library(here)
library(tidyverse)

# RMarkdown
options(digits = 2) # number of decimal digits
opts_chunk$set(
  echo = FALSE, # do not show code
  warning = FALSE, # no package warnings
  message = FALSE # no package messages
)

# custom function for tables
kable_custom <- function(data, caption) {
  knitr::kable(data, digits = getOption("digits"), caption = caption) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
}

```

***
***

```{r all-data}

# load all data
EUR_OS <- readRDS(here("data", "preprocessed", "rds", "CLEAN_OS_Survey_responses.rds")) # all data
EUR_OS_cluster0 <- readRDS(here("data", "preprocessed", "rds", "cluster_0.rds")) # cluster 0
EUR_OS_cluster1 <- readRDS(here("data", "preprocessed", "rds", "cluster_1.rds")) # cluster 1
EUR_OS_cluster2 <- readRDS(here("data", "preprocessed", "rds", "cluster_2.rds")) # cluster 2
EUR_OS_cluster3 <- readRDS(here("data", "preprocessed", "rds", "cluster_3.rds")) # cluster 3
EUR_OS_cluster4 <- readRDS(here("data", "preprocessed", "rds", "cluster_4.rds")) # cluster 4
EUR_OS_cluster5 <- readRDS(here("data", "preprocessed", "rds", "cluster_5.rds")) # cluster 5
EUR_OS_cluster6 <- readRDS(here("data", "preprocessed", "rds", "cluster_6.rds")) # cluster 6
EUR_OS_cluster7 <- readRDS(here("data", "preprocessed", "rds", "cluster_7.rds")) # cluster 7
EUR_OS_cluster8 <- readRDS(here("data", "preprocessed", "rds", "cluster_8.rds")) # cluster 8

```

# Introduction

<!-- The Erasmus Research Institute of Management (ERIM) is committed to making Open Science practices the norm among its researchers. -->

<!-- Open Science increases transparency throughout the research cycle -- from hypothesis, methodology, observation, data collection, to analysis and publication --, resulting in increased research efficiency and enhanced research quality, visibility, and engagement. Open Science also enables the creation of new research questions and promotes collaborations and community building. -->

<!-- For these reasons, ERIM wanted to have a baseline on what and how much open science practices its researchers are already engaging with and which ones they want to learn more about. These questions created the need to conduct a survey. -->

<!-- The ESE and RSM Open Science Spring Survey was open to all researchers from the 6th of April to the 6th of May 2021. Questions were adapted from the [Swinburne Open Science Survey](https://osf.io/vpwf7/). -->

<!-- The survey explored how researchers perceive and use open science practices. Eight main topics were covered: -->

<!-- 1. Preregistration -->
<!-- 2. Open materials/code -->
<!-- 3. Open data -->
<!-- 4. Pre-publication archiving -->
<!-- 5. Open access -->
<!-- 6. General experience with open science practices -->
<!-- 7. Awareness of available tools -->
<!-- 8. Role of ERIM -->

<!-- This report displays the combined results (ESE and RSM) as well as separately for each school[^1]. -->

<!-- This is a living document that will be updated with new information and insights. For any comments or questions, please contact [Dr. Lizette Guzman-Ramirez](mailto:guzmanramirez@rsm.nl) (ERIM Research Data Steward) or [Dr. Antonio Schettino](mailto:schettino@eur.nl) (ERS Open Science Coordinator). -->

# Respondents {.tabset .tabset-pills}

```{r complete-questionnaires}

# percentage of (in)complete surveys
EUR_OS_incomplete <-
  EUR_OS_cluster0 %>% 
  group_by(participant) %>%
  summarize(survey = length(which(Finished == TRUE))/length(Finished)) %>%
  ungroup() %>%
  count(survey) %>% 
  mutate(
    survey = ifelse(survey == 1, "complete", "incomplete"),
    perc = round(n / sum(n) * 100, 2), # calculate percentage
    lab_perc = paste(round(n / sum(n) * 100, 2), "%", sep = "") # percentage as text (for plot labels)
  )

```

A total of `r sum(EUR_OS_incomplete$n)` respondents started the survey, and `r pull(filter(EUR_OS_incomplete, survey == "complete"), n)` completed it. Separate response rates per school, position, and department can be found in the tabs below.

## School

(ref:table-school) Response rate per school.

(ref:footnote-NA) NA indicates no response.

```{r table-school}

EUR_OS_incomplete_school <-
  EUR_OS_cluster0 %>% 
  filter(question == "School") %>% 
  pivot_wider(
    id_cols = c(participant, Finished),
    names_from = question,
    values_from = item
  ) %>%
  group_by(School) %>%
  summarize(
    n = n(),
    perc = round(length(which(Finished == TRUE))/length(Finished) * 100, 2),
    lab_perc = paste(perc, "%", sep = ""),
    .groups = "keep"
  ) %>% 
  arrange(desc(n))

# table
EUR_OS_incomplete_school %>%
  select(-perc) %>% 
  rename("completed survey" = lab_perc) %>% 
  kable_custom(caption = "(ref:table-school)") %>% 
  footnote(
    general = "(ref:footnote-NA)",
    footnote_as_chunk = TRUE
  )

```

## Position

(ref:table-position) Response rate per position.

```{r table-position}

EUR_OS_incomplete_position <-
  EUR_OS_cluster0 %>% 
  filter(question == "Position") %>%
  pivot_wider(
    id_cols = c(participant, Finished),
    names_from = question,
    values_from = item
  ) %>%
  group_by(Position) %>%
  summarize(
    n = n(),
    perc = round(length(which(Finished == TRUE))/length(Finished) * 100, 2),
    lab_perc = paste(perc, "%", sep = ""),
    .groups = "keep"
  ) %>% 
  ungroup() %>% 
  arrange(desc(n))

# table
EUR_OS_incomplete_position %>%
  select(-perc) %>% 
  rename("completed survey" = lab_perc) %>% 
  kable_custom(caption = "(ref:table-position)") %>% 
  footnote(
    general = "(ref:footnote-NA)",
    footnote_as_chunk = TRUE
  )

```

## Department

(ref:table-department) Response rate per department, separately for each school.

```{r table-department}

EUR_OS_incomplete_department <-
  EUR_OS_cluster0 %>% 
  filter(question %in% c("School", "Department")) %>%
  pivot_wider(
    id_cols = c(participant, Finished),
    names_from = question,
    values_from = item
  ) %>%
  group_by(School, Department) %>%
  summarize(
    n = n(),
    perc = round(length(which(Finished == TRUE))/length(Finished) * 100, 2),
    lab_perc = paste(perc, "%", sep = ""),
    .groups = "keep"
  )

# table
EUR_OS_incomplete_department %>%
  select(-perc) %>% 
  rename("completed survey" = lab_perc) %>% 
  kable_custom(caption = "(ref:table-department)") %>% 
  footnote(
    general = "(ref:footnote-NA)",
    footnote_as_chunk = TRUE
  )

```

# {-}

# Open Access {.tabset .tabset-pills}

## EUR

###################################
# CONTINUE FROM HERE
###################################

```{r oa-data}

EUR_OS_open_access <-
  EUR_OS_cluster1 %>% 
  filter(Finished == TRUE) %>% 
  droplevels()

```

```{r oa-data-importance}

EUR_OS_open_access_importance <-
  EUR_OS_open_access %>% 
  filter(question %in% c("School",
                         "In your opinion, how important is Open Access for your work?")
                         ) %>%
  droplevels() %>% 
  mutate( # order levels
    item = fct_explicit_na(item, "NA"),
    item = fct_relevel( # relevel or reorder?
      item, 
      "Extremely important", 
      "Very important",
      "Moderately important",
      "Slightly important", 
      "Not at all important",
      "I don’t know/prefer not to answer",
      "NA"
      )
    ) %>% 
  filter(item != "NA") %>% 
    pivot_wider(
    id_cols = participant,
    names_from = question,
    values_from = item
  ) %>%
  group_by(School) %>%
  summarize(
    n = n(),
    perc = round(length(which(Finished == TRUE))/length(Finished) * 100, 2),
    lab_perc = paste(perc, "%", sep = ""),
    .groups = "keep"
  )
  
  
  
  
  arrange(desc(perc))

```




From the question *`r ERIM_OS_data_importance$question[1]`*, `r paste0(format(sum(ERIM_OS_data_importance[1, "perc"], ERIM_OS_data_importance[2, "perc"], ERIM_OS_data_importance[3, "perc"]), digits = 0), "%")` of respondents think that using open materials and/or code is *`r ERIM_OS_data_importance$item[1]`*, *`r ERIM_OS_data_importance$item[2]`*, or *`r ERIM_OS_data_importance$item[3]`*, whereas `r paste0(pull(filter(ERIM_OS_data_importance, item == "Not at all important"), "perc"), "%")` think it is *`r pull(filter(ERIM_OS_data_importance, item == "Not at all important"), item)`* (see Figure \@ref(fig:figure7)).







